---
title: "STA302 Final Project"
output:
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage{xeCJK}
  - \setCJKmainfont{SimSun} 
---
```{r}
library(dplyr)


df <- read.csv("../data/ames_cleaned.csv")


if (!("Age_Remodel" %in% names(df)) &&
all(c("Year_Sold", "Year_Remod_Add") %in% names(df))) {
df$Age_Remodel <- df$Year_Sold - df$Year_Remod_Add
}


if ("Age_Remodel" %in% names(df)) {
df <- df[df$Age_Remodel >= 0, ]
}

dim(df)
head(df[, c("Sale_Price","Age_Remodel")])

```
```{r}
set.seed(302) 

n <- nrow(df)
train_prop <- 0.8
train_idx  <- sample(seq_len(n), size = floor(train_prop * n))

train <- df[train_idx, ]
test  <- df[-train_idx, ]

dim(train); dim(test)

```

```{r}
# create Bldg_Type2（OneFam vs Non1Fam）in train / test

train <- train %>%
mutate(Bldg_Type2 = ifelse(as.character(Bldg_Type) == "OneFam",
"OneFam", "Non1Fam"),
Bldg_Type2 = factor(Bldg_Type2, levels = c("OneFam","Non1Fam")))

test <- test %>%
mutate(Bldg_Type2 = ifelse(as.character(Bldg_Type) == "OneFam",
"OneFam", "Non1Fam"),
Bldg_Type2 = factor(Bldg_Type2, levels = c("OneFam","Non1Fam")))

# build Sale_Price model within train only

model_train <- lm(
Sale_Price ~ Gr_Liv_Area + Mas_Vnr_Area + Age_Remodel +
Bedroom_AbvGr + Total_Bsmt_SF + Garage_Cars +
Full_Bath + Fireplaces + Bldg_Type2 +
Gr_Liv_Area:Bldg_Type2,
data = train
)

summary(model_train)

```

```{r}
y_obs_train <- model.response(model.frame(model_train))
y_hat_train <- fitted(model_train)
resid_train <- resid(model_train)

c(length(y_obs_train), length(y_hat_train), length(resid_train))

```

```{r}
plot(y_hat_train, y_obs_train,
pch = 16, cex = 0.5,
xlab = "Fitted values (train)",
ylab = "Observed Sale_Price (train)",
main = "Observed vs Fitted (train)")
abline(0, 1, col = "red", lwd = 2, lty = 2)              
lines(lowess(y_hat_train, y_obs_train), col = "blue", lwd = 2)  # LOESS curve

```

```{r}
plot(y_hat_train, resid_train,
pch = 16, cex = 0.5,
xlab = "Fitted values (train)",
ylab = "Residuals",
main = "Residuals vs Fitted (train)")
abline(h = 0, col = "red", lwd = 2)
lines(lowess(y_hat_train, resid_train), col = "blue", lwd = 2)

```

```{r}
num_x <- c("Gr_Liv_Area","Mas_Vnr_Area","Age_Remodel","Bedroom_AbvGr",
"Total_Bsmt_SF","Garage_Cars","Full_Bath","Fireplaces")

par(mfrow = c(3,3), mar = c(4,4,2,1))
for (v in num_x) {
x <- train[[v]]
plot(x, resid_train,
pch = 16, cex = 0.5,
xlab = v, ylab = "Residuals",
main = paste("Residuals vs", v))
abline(h = 0, col = "red", lwd = 2)
lines(lowess(x, resid_train), col = "blue", lwd = 2)
}

# Residuals by Bldg_Type2

boxplot(resid_train ~ train$Bldg_Type2,
xlab = "Bldg_Type2", ylab = "Residuals",
main = "Residuals by Bldg_Type2")
abline(h = 0, col = "red", lwd = 2)
par(mfrow = c(1,1))

```

```{r}
qqnorm(resid_train,
main = "Normal Q-Q Plot of Residuals (train)")
qqline(resid_train, col = "red", lwd = 2)

```
```{r}
C2_data <- train[, num_x]

pairs(C2_data,
pch = 16, cex = 0.3,
main = "C2: Pairwise Scatterplots of Predictors (train)")

```



---


```{r boxcox_Y_and_X, echo=TRUE, message=FALSE, warning=FALSE}
library(MASS)

## 4.1 对 Y 做 Box–Cox
bc <- boxcox(model_train, lambda = seq(-0.5, 0.5, by = 0.05))

lambda_y_hat <- bc$x[which.max(bc$y)]   # 真正的最优 λ（写在报告里）
lambda_y_hat

lambda_y <- 0.25                        # 模型里实际使用的 λ（四次方根）

# Box–Cox 通用变换函数
bc_transform <- function(x, lambda) {
  if (abs(lambda) < 1e-6) {
    log(x)
  } else {
    (x^lambda - 1) / lambda
  }
}

# 生成变换后的响应变量 Y_bc
train$Y_bc <- bc_transform(train$Sale_Price, lambda_y)
y_bc <- train$Y_bc   # 方便后面 lm 使用

## 4.2 对每个 X 单独做 Box–Cox，先记录 λ 到 lambda_list（用于决定怎么近似）
predictor_names <- c("Gr_Liv_Area", "Total_Bsmt_SF", "Mas_Vnr_Area",
                     "Age_Remodel", "Bedroom_AbvGr", "Garage_Cars",
                     "Full_Bath", "Fireplaces")

lambda_list <- numeric(length(predictor_names))
names(lambda_list) <- predictor_names

for (v in predictor_names) {

  x <- train[[v]]

  # Box-Cox 要求 >0，有 0 或负数就整体 +1（只在变换时用）
  if (any(x <= 0)) {
    x_use <- x + 1
  } else {
    x_use <- x
  }

  # 对单个 predictor 做 Box–Cox：Y_bc ~ x_use
  bc_x <- boxcox(
    lm(y_bc ~ x_use),
    lambda = seq(-0.5, 0.5, by = 0.05),
    plotit = FALSE
  )

  best_lambda <- bc_x$x[which.max(bc_x$y)]
  lambda_list[v] <- best_lambda
}

lambda_list
```


```{r manual_transform_X, echo=TRUE}

## 手动根据 lambda_list 做变换（可解释性更好）

# 变换规则：
#  λ ≈ 0.50 → sqrt()
#  λ ≈ 0.05 → log()
#  λ ≈ 0.35 → 立方根（1/3 次方）
#  λ ≈ 0.25 → 四次方根（1/4 次方）

### -------- 1) λ ≈ 0.50  → sqrt() --------
train$Gr_Liv_Area_bc    <- sqrt(train$Gr_Liv_Area)
train$Total_Bsmt_SF_bc  <- sqrt(train$Total_Bsmt_SF)
train$Mas_Vnr_Area_bc   <- sqrt(train$Mas_Vnr_Area)

### -------- 2) λ ≈ 0.05 → log() --------
# 防止 0 值报错，统一 +1 再 log
train$Age_Remodel_bc    <- log(train$Age_Remodel + 1)
train$Bedroom_AbvGr_bc  <- log(train$Bedroom_AbvGr + 1)

### -------- 3) λ ≈ 0.35 → 立方根 --------
train$Garage_Cars_bc    <- (train$Garage_Cars)^(1/3)

### -------- 4) λ ≈ 0.25 → 四次方根 --------
train$Full_Bath_bc      <- (train$Full_Bath)^(1/4)
train$Fireplaces_bc     <- (train$Fireplaces)^(1/4)

## 输出检查
summary(train[, c("Gr_Liv_Area_bc","Total_Bsmt_SF_bc","Mas_Vnr_Area_bc",
                  "Age_Remodel_bc","Bedroom_AbvGr_bc","Garage_Cars_bc",
                  "Full_Bath_bc","Fireplaces_bc")])

```

```{r}
model_bc <- lm(
Y_bc ~ Gr_Liv_Area_bc + Mas_Vnr_Area_bc + Age_Remodel_bc +
Bedroom_AbvGr_bc + Total_Bsmt_SF_bc + Garage_Cars_bc +
Full_Bath_bc + Fireplaces_bc + Bldg_Type2 +
Gr_Liv_Area_bc:Bldg_Type2,
data = train
)

summary(model_bc)

```

```{r}
y_hat_bc <- fitted(model_bc)
resid_bc <- resid(model_bc)

c(length(y_hat_bc), length(resid_bc), length(train$Y_bc))

```

```{r}
y_obs_bc <- train$Y_bc

plot(y_hat_bc, y_obs_bc,
pch = 16, cex = 0.5,
xlab = "Fitted values (Box–Cox model, train)",
ylab = "Observed Y_bc",
main = "Observed vs Fitted (Box–Cox, train)")
abline(0, 1, col = "red", lwd = 2, lty = 2)
lines(lowess(y_hat_bc, y_obs_bc), col = "blue", lwd = 2)

```

```{r}
plot(y_hat_bc, resid_bc,
pch = 16, cex = 0.5,
xlab = "Fitted values (Box–Cox model, train)",
ylab = "Residuals",
main = "Residuals vs Fitted (Box–Cox, train)")
abline(h = 0, col = "red", lwd = 2)
lines(lowess(y_hat_bc, resid_bc), col = "blue", lwd = 2)

```

```{r}
bc_vars <- paste0(predictor_names, "_bc")

par(mfrow = c(3,3), mar = c(4,4,2,1))

# 1–8：数值型 X_bc

for (v in bc_vars) {
plot(train[[v]], resid_bc,
pch = 16, cex = 0.5,
xlab = v,
ylab = "Residuals",
main = paste("Residuals vs", v))
abline(h = 0, col = "red")
lines(lowess(train[[v]], resid_bc), col = "blue", lwd = 1.5)
}

# 第9张：Bldg_Type2

boxplot(resid_bc ~ train$Bldg_Type2,
xlab = "Bldg_Type2",
ylab = "Residuals",
main = "Residuals by Bldg_Type2 (Box–Cox)",
col = c("lightgrey","lightblue"))
abline(h = 0, col = "red", lwd = 2)

par(mfrow = c(1,1))

```

```{r}
qqnorm(resid_bc,
main = "Normal Q-Q Plot of Residuals (Box–Cox model)")
qqline(resid_bc, col = "red", lwd = 2)

```

```{r}
bc_data <- train[, bc_vars]

pairs(bc_data,
pch = 16, cex = 0.3,
main = "C2: Pairwise Scatterplots of Predictors (Box–Cox transformed)")

```

```{r}
library(car)

# VIF for full transformed model
vif_bc <- vif(model_bc)
vif_bc

# Correlation matrix for transformed numeric predictors
bc_vars <- c("Gr_Liv_Area_bc", "Total_Bsmt_SF_bc", "Mas_Vnr_Area_bc",
             "Age_Remodel_bc", "Bedroom_AbvGr_bc", "Garage_Cars_bc",
             "Full_Bath_bc", "Fireplaces_bc")

cor_bc <- cor(train[, bc_vars])
round(cor_bc, 3)
```
```{r}
# Overall F-test: does the model explain Y_bc better than no predictors?
mod0_bc <- lm(Y_bc ~ 1, data = train)       # null model with intercept only
anova(mod0_bc, model_bc)
```

```{r}
summary(model_bc)
```

```{r}
#Test whether interaction term is needed 
model_bc_no_int <- lm(
  Y_bc ~ Gr_Liv_Area_bc + Mas_Vnr_Area_bc + Age_Remodel_bc +
    Bedroom_AbvGr_bc + Total_Bsmt_SF_bc + Garage_Cars_bc +
    Full_Bath_bc + Fireplaces_bc + Bldg_Type2,
  data = train
)

anova(model_bc_no_int, model_bc) 
```
```{r}
#Test dropping the “bedroom” variable, since it overlaps with size and baths.
model_bc_no_bedroom <- lm(
  Y_bc ~ Gr_Liv_Area_bc + Mas_Vnr_Area_bc + Age_Remodel_bc +
    Total_Bsmt_SF_bc + Garage_Cars_bc + Full_Bath_bc +
    Fireplaces_bc + Bldg_Type2 + Gr_Liv_Area_bc:Bldg_Type2,
  data = train
)

anova(model_bc_no_bedroom, model_bc)
```

```{r}
#Test dropping the “bedroom” variable, since it overlaps with size and baths.
model_bc_no_amen <- lm(
  Y_bc ~ Gr_Liv_Area_bc + Mas_Vnr_Area_bc + Age_Remodel_bc +
    Bedroom_AbvGr_bc + Total_Bsmt_SF_bc + Bldg_Type2 +
    Gr_Liv_Area_bc:Bldg_Type2,
  data = train
)

anova(model_bc_no_amen, model_bc)
```
```{r}
library(MASS)

step_bc_back <- stepAIC(
  model_bc,
  direction = "backward",  # start from full and only drop
  trace = TRUE            # set TRUE if you want to see each step printed
)

summary(step_bc_back)
```
```{r}
step_bc_step <- stepAIC(model_bc, direction = "both", trace = FALSE)
summary(step_bc_step)
```
```{r}
#BIC 
n_train <- nrow(train)

step_bc_BIC <- stepAIC(
  model_bc,
  direction = "backward",
  k = log(n_train),
  trace = FALSE
)

summary(step_bc_BIC)
```
```{r}
# AIC(model_bc, step_bc)
# BIC(model_bc, step_bc)
# 
# c(
#   full    = summary(model_bc)$adj.r.squared,
#   stepAIC = summary(step_bc)$adj.r.squared
# )
# c(
#   full    = summary(model_bc)$adj.r.squared,
#   stepAIC = summary(step_bc)$adj.r.squared
# )

model_bc

step_bc_back

step_bc_step

step_bc_BIC
```
# influential points

```{r}
# pick one (all same) to be the final model
final_bc <- model_bc   

# sample & predictor numbers
n_bc <- nrow(train)
p_bc <- length(coef(final_bc)) - 1

# cutoffs
h_cut    <- 2 * (p_bc + 1) / n_bc
cook_cut <- qf(0.5, df1 = p_bc + 1, df2 = n_bc - p_bc - 1)
fit_cut  <- 2 * sqrt((p_bc + 1) / n_bc)
beta_cut <- 2 / sqrt(n_bc)

# diagnose variables
h_ii      <- hatvalues(final_bc)         # leverage
r_std     <- rstandard(final_bc)         # standardized residuals
cook_d    <- cooks.distance(final_bc)    # Cook's distance
dffits_i  <- dffits(final_bc)            # DFFITS
dfbetas_i <- dfbetas(final_bc)           # DFBETAS (矩阵)

# problematic points
lev_pts    <- which(h_ii > h_cut)                    
outliers   <- which(r_std > 4 | r_std < -4)         
cook_infl  <- which(cook_d > cook_cut)              
fit_infl   <- which(abs(dffits_i) > fit_cut)         

cat("leverage points \n", lev_pts, "\n\n")
cat("outliers \n", outliers, "\n\n")
cat("cook distance influential \n", cook_infl, "\n\n")
cat("DFFITS influential \n", fit_infl, "\n\n")

# debetas
for (j in 1:ncol(dfbetas_i)) {
  cat("DFBETAS for beta", colnames(dfbetas_i)[j], ":\n")
  print(which(abs(dfbetas_i[, j]) > beta_cut))
  cat("\n")
}

```


```{r}
## find how many influential points are in at least 3 categories
is_lev    <- h_ii > h_cut
is_out    <- (r_std > 4 | r_std < -4)
is_cook   <- cook_d > cook_cut
is_dffits <- abs(dffits_i) > fit_cut

flag_count <- is_lev + is_out + is_cook + is_dffits

idx_3plus <- which(flag_count >= 3)
idx_3plus

# find their dfbeta count
dfb_flag <- abs(dfbetas_i) > beta_cut 
dfb_count <- rowSums(dfb_flag)


# summary table
infl_summary <- data.frame(
  id         = idx_3plus,
  n_flags    = flag_count[idx_3plus],
  n_badbetas = dfb_count[idx_3plus],
  leverage   = is_lev[idx_3plus],
  outlier    = is_out[idx_3plus],
  cook       = is_cook[idx_3plus],
  dffits     = is_dffits[idx_3plus]
)
infl_summary


```

# test
```{r}
# do the same transformation on test

test$Gr_Liv_Area_bc   <- sqrt(test$Gr_Liv_Area)
test$Total_Bsmt_SF_bc <- sqrt(test$Total_Bsmt_SF)
test$Mas_Vnr_Area_bc  <- sqrt(test$Mas_Vnr_Area)

test$Age_Remodel_bc   <- log(test$Age_Remodel + 1)
test$Bedroom_AbvGr_bc <- log(test$Bedroom_AbvGr + 1)

test$Garage_Cars_bc   <- (test$Garage_Cars)^(1/3)
test$Full_Bath_bc     <- (test$Full_Bath)^(1/4)
test$Fireplaces_bc    <- (test$Fireplaces)^(1/4)

test$Y_bc <- bc_transform(test$Sale_Price, lambda_y)


summary(test[, c("Y_bc", "Gr_Liv_Area_bc","Total_Bsmt_SF_bc","Mas_Vnr_Area_bc",
                 "Age_Remodel_bc","Bedroom_AbvGr_bc","Garage_Cars_bc",
                 "Full_Bath_bc","Fireplaces_bc")])


```

```{r}

# prediction of train set
pred_train_bc <- predict(final_bc, newdata = train)

# predicttion of test set
pred_test_bc  <- predict(final_bc, newdata = test)

# MSE
mse_train_bc <- mean((train$Y_bc - pred_train_bc)^2)
mse_test_bc  <- mean((test$Y_bc  - pred_test_bc)^2)

mse_train_bc
mse_test_bc

```
```{r}
summary(model_bc)
```


```{r}
bc_inverse <- function(y_bc, lambda = 0.25) {
  (lambda * y_bc + 1)^ (1 / lambda)
}

# go back to original housing price
pred_train_price <- bc_inverse(pred_train_bc, lambda = 0.25)
pred_test_price  <- bc_inverse(pred_test_bc,  lambda = 0.25)

mse_train_bc
mse_test_bc
mean(pred_train_bc)
mean(pred_test_bc)
mean(pred_train_price)
mean(pred_test_price)

mse_train_price  <- mean((train$Sale_Price - pred_train_price)^2)
mse_test_price   <- mean((test$Sale_Price  - pred_test_price)^2)

rmse_train_price <- sqrt(mse_train_price)
rmse_test_price  <- sqrt(mse_test_price)

rmse_train_price
rmse_test_price
```

```{r}
rmse_train_bc <- sqrt(mse_train_bc)
rmse_test_bc  <- sqrt(mse_test_bc)
sd_ybc        <- sd(train$Y_bc)

rmse_train_bc
rmse_test_bc
sd_ybc
rmse_train_bc / sd_ybc
rmse_test_bc  / sd_ybc

```

On the Box–Cox–transformed scale, the training and test MSEs are 12.95 and 12.96 (RMSE ≈ 3.60), which correspond to about 43% of the standard deviation of the transformed response. This indicates that the model explains a meaningful portion of the variation in sale prices, but there is still substantial unexplained variability.

On the original price scale, the training and test RMSEs are approximately $36,000 and $31,500, respectively. The fact that the test error is very close to the training error suggests that the model does not overfit severely and generalizes reasonably well to new data, although the prediction errors remain non-trivial in economic terms.


# 
```{r}
# training model
mod_train <- final_bc  

mod_test <- lm(
  Y_bc ~ Gr_Liv_Area_bc + Mas_Vnr_Area_bc + Age_Remodel_bc +
    Bedroom_AbvGr_bc + Total_Bsmt_SF_bc + Garage_Cars_bc +
    Full_Bath_bc + Fireplaces_bc + Bldg_Type2 +
    Gr_Liv_Area_bc:Bldg_Type2,
  data = test
)

p      <- length(coef(mod_train)) - 1   # 10 predictors
n_tr   <- nrow(train)
n_te   <- nrow(test)

hcut_tr  <- 2 * (p + 1) / n_tr
hcut_te  <- 2 * (p + 1) / n_te

cookcut_tr <- qf(0.5, df1 = p + 1, df2 = n_tr - p - 1)
cookcut_te <- qf(0.5, df1 = p + 1, df2 = n_te - p - 1)

fitcut_tr  <- 2 * sqrt((p + 1) / n_tr)
fitcut_te  <- 2 * sqrt((p + 1) / n_te)


# training set
n_lev_tr   <- length(which(hatvalues(mod_train) > hcut_tr))
n_out_tr   <- length(which(abs(rstandard(mod_train)) > 4))
n_cook_tr  <- length(which(cooks.distance(mod_train) > cookcut_tr))
n_dffits_tr<- length(which(abs(dffits(mod_train)) > fitcut_tr))

cbind(n_lev_tr, n_out_tr, n_cook_tr, n_dffits_tr)

# test set
n_lev_te   <- length(which(hatvalues(mod_test) > hcut_te))
n_out_te   <- length(which(abs(rstandard(mod_test)) > 4))
n_cook_te  <- length(which(cooks.distance(mod_test) > cookcut_te))
n_dffits_te<- length(which(abs(dffits(mod_test)) > fitcut_te))

cbind(n_lev_te, n_out_te, n_cook_te, n_dffits_te)

```
When we refit the final model on the test set and counted high-leverage points, extreme standardized residuals and large DFFITS using the same cutoffs, the proportions of flagged observations were similar in the training and test sets (e.g., 222 vs 53 high-leverage points and 142 vs 52 large-DFFITS points under an 80/20 split). This suggests that potentially problematic observations are not unique to one split of the data, although our main influential-point analysis is based on the training sample.



```{r influence_plot, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)

diag_long <- tibble(
  Set    = rep(c("Training", "Test"), each = 4),
  Metric = rep(c("High leverage",
                 "|St. resid| > 4",
                 "Cook's D",
                 "|DFFITS|"), times = 2),
  n      = c(rep(n_tr, 4), rep(n_te, 4)),
  Count  = c(
    n_lev_tr,    n_out_tr,    n_cook_tr,    n_dffits_tr,
    n_lev_te,    n_out_te,    n_cook_te,    n_dffits_te
  )
) %>%
  mutate(Percent = 100 * Count / n)

ggplot(diag_long, aes(x = Metric, y = Percent, fill = Set)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_text(aes(label = paste0(Count, " (", round(Percent, 1), "%)")),
            position = position_dodge(width = 0.7),
            vjust = -0.4, size = 3) +
  scale_y_continuous(
    name   = "Percent of observations",
    expand = expansion(mult = c(0, 0.15))
  ) +
  scale_fill_manual(values = c("Training" = "#4E79A7",
                               "Test"     = "#A0CBE8")) +
  labs(
    x = NULL,
    title = "Potentially problematic observations\nin training and test sets"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    legend.position      = "top",
    panel.grid.major.x   = element_blank(),
    axis.text.x          = element_text(angle = 20, hjust = 1),
    plot.title           = element_text(hjust = 0.5)
  )


```

```{r final_model_table, echo=FALSE}
## 0. Recreate pred_order from the full model ----
full_mod   <- model_bc
pred_order <- attr(terms(full_mod), "term.labels") # 提取自变量名字

## 1. Main model-selection table with short codes ----
pred_codes <- paste0("x", seq_along(pred_order))   # x1, x2, ...

# Model labels: Y_bc = β0 + ε, Y_bc = β0 + β1x1 + ε, ...
model_labels <- c(
  "Y_bc = β0 + ε",
  paste0(
    "Y_bc = β0 + ",
    sapply(1:length(pred_order), function(k) {
      paste0("β", 1:k, "x", 1:k, collapse = " + ")
    }),
    " + ε"
  )
)

# Predictors shown as codes: x1, x1, x2, ...
pred_labels_code <- c(
  "None (intercept only)",
  sapply(1:length(pred_order), function(k) {
    paste(pred_codes[1:k], collapse = ", ")
  })
)

# Extract metrics
rss_vals    <- sapply(fits, deviance)
aic_vals    <- sapply(fits, AIC)
bic_vals    <- sapply(fits, BIC)
adj_r2_vals <- as.numeric(sapply(fits, function(m) summary(m)$adj.r.squared))

model_sel_table <- data.frame(
  Model            = model_labels,
  p                = 0:length(pred_order),
  RSS              = rss_vals,
  AIC              = aic_vals,
  BIC              = bic_vals,
  Adj_R2           = round(adj_r2_vals, 2),
  Predictors_codes = pred_labels_code,
  row.names        = NULL
)

library(kableExtra)

model_sel_table |>
  kbl(
    caption = "Summary of nested candidate models with RSS, AIC, BIC and adjusted R^2.",
    digits  = 2,
    align   = c("l", "c", "r", "r", "r", "c")
  ) |>
  kable_styling(
    full_width = FALSE,
    position   = "center",
    font_size  = 9
  ) |>
  column_spec(1, width = "4cm") |>
  column_spec(6, width = "3cm")

```





```{r}
## 2. Codebook: what does x0, x1, x2, ... mean? ----

# 1) 先根据最终 full_mod 拿到真正用到的自变量顺序
pred_order <- attr(terms(full_mod), "term.labels")

# 2) 自变量说明字典
desc_map <- c(
  Gr_Liv_Area_bc               = "Above–ground living area (Box–Cox)",
  Total_Bsmt_SF_bc             = "Total basement area (Box–Cox)",
  Mas_Vnr_Area_bc              = "Masonry veneer area (Box–Cox)",
  Age_Remodel_bc               = "Remodel age (years since remodel, Box–Cox)",
  Bedroom_AbvGr_bc             = "Bedrooms above ground (Box–Cox)",
  Garage_Cars_bc               = "Garage capacity (number of cars, Box–Cox)",
  Full_Bath_bc                 = "Number of full bathrooms (Box–Cox)",
  Fireplaces_bc                = "Number of fireplaces (Box–Cox)",
  Bldg_Type2                   = "Building type: non–single family (indicator)",
  "Gr_Liv_Area_bc:Bldg_Type2"  = "Interaction: Above–ground living area × Building type"
)

pred_names_readable <- unname(desc_map[pred_order])
pred_codes <- paste0("x", seq_along(pred_order))

# 3) 先做自变量部分
codebook_pred <- data.frame(
  Code        = pred_codes,
  Variable    = pred_order,
  Description = pred_names_readable
)

# 4) 再单独加一行响应变量 y
codebook_y <- data.frame(
  Code        = "y",
  Variable    = "Y_bc",
  Description = "Box–Cox transformed sale price: (Sale_Price^0.25 - 1) / 0.25"
)

# 5) 合在一起，y 放最上面
codebook <- rbind(codebook_y, codebook_pred)

library(kableExtra)

codebook |>
  kbl(
    caption = "Mapping between response/predictor codes (y, x1, ..., xk) and variables used in the model.",
    align   = c("c", "l", "l")
  ) |>
  kable_styling(
    full_width = FALSE,
    position   = "center",
    font_size  = 9
  )

```



